A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-12-21 paper/submission/ZW10157-response-1.tex
adding in Ref B suggestions to abstract, etc

In this paper, we present the implementation of such a general-purpose
framework for simulation-based multi-objective optimization methods
that allows the automatic investigation of optimal sets of machine
parameters. The implementation is based on a master/slave paradigm,
employing several masters that govern a set of slaves executing
simulations and performing optimization tasks. -> In this paper, we
present a general-purpose framework for simulation-based
multi-objective optimization methods that allows the automatic
investigation of optimal sets of machine parameters.

The high charge beam line at the Argonne Wakefield Accelerator
Facility was used as the beam dynamics model. The 3D beam size,
transverse momentum, and energy spread were optimized. Please state
the significance of the optimization. Is the solution found better
than the original design? Then provide a comparison with the baseline
solution as Bazarov and Sinclair did in their 2005 paper. Is it the
first such solution for the AWA? Then make that clear. Has this
solution been used in the machine? Then provide a comparison between
prediction and operational experience.

Section I

line 35: trade of -$>$ trade off

@@

Section II

lines 53-74. The car example is from Deb’s book but not cited. This
example can probably be removed as EA/GA methodology is established
practice now.

Section III

subsection A

Needs to be updated to reflect developments in accelerator physics.

subsections B-F

Replace with a brief overview and put the details in Supplemental
Material

>>>>

In this paper, we present the implementation of such a general-purpose
framework for simulation-based multi-objective optimization methods
that allows the automatic investigation of optimal sets of machine
parameters. The implementation is based on a master/slave paradigm,
employing several masters that govern a set of slaves executing
simulations and performing optimization tasks. $->$ In this paper, we
present a general-purpose framework for simulation-based
multi-objective optimization methods that allows the automatic
investigation of optimal sets of machine parameters.

{\bf Our Response:} {\color{blue} The suggested edit above has been incorporated into the updated manuscript. }

The high charge beam line at the Argonne Wakefield Accelerator
Facility was used as the beam dynamics model. The 3D beam size,
transverse momentum, and energy spread were optimized.

Please state
the significance of the optimization. Is the solution found better
than the original design? Then provide a comparison with the baseline
solution as Bazarov and Sinclair did in their 2005 paper. Is it the
first such solution for the AWA? Then make that clear. Has this
solution been used in the machine? Then provide a comparison between
prediction and operational experience.

Section I, line 35: trade of -$>$ trade off

@@

Section II:
lines 53-74. The car example is from Deb’s book but not cited. This
example can probably be removed as EA/GA methodology is established
practice now.

{\bf Our response:} {\color{blue} This example has been removed.}

Section III, subsection A:
Needs to be updated to reflect developments in accelerator physics.

{\bf Our response:} {\color{blue} XXX}

subsections B-F:
Replace with a brief overview and put the details in Supplemental
Material

{\bf Our response: } {\color{blue} XXX}

### 2018-12-21 paper/submission/prab.tex
adding in Ref B suggestions to abstract, etc

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.
We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame a fast 
  and scalable software framework is required.
In this paper, we present the implementation of such a general-purpose
  framework for simulation-based multi-objective optimization methods that
  allows the automatic investigation of optimal sets of machine parameters.
The implementation is based on a master/slave paradigm, employing several
  masters that govern a set of slaves executing simulations and performing
  optimization tasks.
Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
  forward solver, validation experiments and 
 results of multi-objective optimization problems in the domain of beam
  dynamics are presented. The high charge beam line at the Argonne Wakefield 
  Accelerator Facility was used as the beam dynamics model. The 3D beam size, 
  transverse momentum, and energy spread were optimized.

@@

Often, conflicting objectives are encountered, and this complicates the concept of
  optimality.
To illustrate this, let us consider the problem of buying a car.
Naturally, we try to bargain the lowest price for the best performance,
  e.g.\ maximal horsepower or minimal fuel consumption.
This can be formulated as MOOP (\ref{eq:car-moop}).
%
\begin{equation}
  \begin{array}{cl}
  \min          & \quad \left[ \text{price}, -\text{performance} \right]^T \\
    \text{s.t.} & \quad \text{low}_\text{pr} \leq \text{price} \leq \text{high}_\text{pr}\\
                & \quad \text{low}_\text{pe} \leq \text{performance} \leq \text{high}_\text{pe}
  \end{array}
  \label{eq:car-moop}
\end{equation}

@@

In general, it is not possible to get the maximal performance for the lowest
  price and a trade off decision between performance and price has to be
  reached (see Fig.~\ref{fig:tradeoff}).
Since not every choice is equally profitable for the buyer (for example, car
  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
  trade offs (red points) that are essentially ``equally optimal'' in both
  conflicting objectives, meaning, we cannot improve one point without hurting
  at least one other solution.
This is known as \textit{Pareto optimality}.
The set of Pareto optimal points (blue curve) forms the Pareto front or
  surface.
All points on this surface are considered to be Pareto optimal.

>>>>

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.
We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame a fast 
  and scalable software framework is required.
In this paper, we
present a general-purpose framework for simulation-based
multi-objective optimization methods that allows the automatic
investigation of optimal sets of machine parameters.
Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
  forward solver, validation experiments and 
 results of multi-objective optimization problems in the domain of beam
  dynamics are presented. The high charge beam line at the Argonne Wakefield 
  Accelerator Facility was used as the beam dynamics model. The 3D beam size, 
  transverse momentum, and energy spread were optimized.

@@

Often, conflicting objectives are encountered, and this complicates the concept of
  optimality.

  \iffalse
To illustrate this, let us consider the problem of buying a car.
Naturally, we try to bargain the lowest price for the best performance,
  e.g.\ maximal horsepower or minimal fuel consumption.
This can be formulated as MOOP (\ref{eq:car-moop}).
%
\begin{equation}
  \begin{array}{cl}
  \min          & \quad \left[ \text{price}, -\text{performance} \right]^T \\
    \text{s.t.} & \quad \text{low}_\text{pr} \leq \text{price} \leq \text{high}_\text{pr}\\
                & \quad \text{low}_\text{pe} \leq \text{performance} \leq \text{high}_\text{pe}
  \end{array}
  \label{eq:car-moop}
\end{equation}

@@

In general, it is not possible to get the maximal performance for the lowest
  price and a trade off decision between performance and price has to be
  reached (see Fig.~\ref{fig:tradeoff}). 
Since not every choice is equally profitable for the buyer (for example, car
  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
  trade offs (red points) that are essentially ``equally optimal'' in both
  conflicting objectives, meaning, we cannot improve one point without hurting
  at least one other solution.
  \fi
This is known as \textit{Pareto optimality}.
The set of Pareto optimal points (blue curve) forms the Pareto front or
  surface.
All points on this surface are considered to be Pareto optimal.
